---
title: "LowerBoiseBCGCalc-NEWS"
author: "Ben.Block@tetratech.com"
date: "`r Sys.time()`"
output: github_document
  #md_document:
   # variant: markdown_github
---

<!-- NEWS.md is generated from NEWS.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "NEWS-"
)
```

```{r, echo = FALSE}
cat(paste0("Last Update: ",Sys.time()))
```

# LowerBoiseBCGCalc 0.0.0.9010 (2026-05-21)

* refactor: Update UI
   + Hide unwanted tabs

# LowerBoiseBCGCalc 0.0.0.9009 (2026-05-21)

* refactor: Modify BCG_3metmemb_xtab columns
* refactor: Modify order of columns in BCG Results file
* fix: Modify QC check for missing INDEX_NAME in File Builder

# LowerBoiseBCGCalc 0.0.0.9008 (2026-05-20)

* docs: Add shiny app URL to readme

# LowerBoiseBCGCalc 0.0.0.9007 (2026-05-20)

* refactor: Update age class xtab for RIS == TRUE
* refactor: Add membership xtab to BCG results

# LowerBoiseBCGCalc 0.0.0.9006 (2026-05-20)

* fix: Update BCGcalc package for update to Fish Main_Exckert rules

# LowerBoiseBCGCalc 0.0.0.9005 (2026-05-20)

* refactor: Add cross tab table for age class to fish output for file builder

# LowerBoiseBCGCalc 0.0.0.9004 (2026-05-20)

* docs: Add missing packages to global.R
    + kableExtra
    + rsconnect
    
# LowerBoiseBCGCalc 0.0.0.9003 (2026-05-20)

* refactor: Update version number to global
* refactor: Use revised versions of packages
    + BioMonTools
    + BCGcalc
* docs: Add "_tests" folder
* docs: Add "_tests" folder to gitignore
* refactor: Update error catching for mismatch or blank Index_Name
    + Bugs and Fish
    + FileBuilder and BCG Calculation

# LowerBoiseBCGCalc 0.0.0.9002 (2026-02-01)

-   Added File Builder function to join fish lengths to age via lookup
    
# LowerBoiseBCGCalc 0.0.0.9000 (2025-12-31)

-   Created GitHub repository
-   docs: Add base package files from GreatPlainsBCGCalc (Blocktt)
    -   DESCRIPTION
    -   NEWS
    -   README
    -   app function
