---
title: "LowerBoiseBCGCalc-NEWS"
author: "Ben.Block@tetratech.com"
date: "`r Sys.time()`"
output: github_document
  #md_document:
   # variant: markdown_github
---

<!-- NEWS.md is generated from NEWS.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "NEWS-"
)
```

```{r, echo = FALSE}
cat(paste0("Last Update: ",Sys.time()))
```

# LowerBoiseBCGCalc 0.0.0.9032 (2026-08-04)

* refactor: Added location, activity year, and activity date to all outputs

# LowerBoiseBCGCalc 0.0.0.9031 (2026-07-21)

* refactor: merge clean up

# LowerBoiseBCGCalc 0.0.0.9030 (2026-07-21)

* refactor: Update BioMonTools package
* refactor: Update Shiny prep code

# LowerBoiseBCGCalc 0.0.0.9029 (2026-07-10)

* docs: Updates to documentation

# LowerBoiseBCGCalc 0.0.0.9028 (2026-07-09)

* refactor: Added new output for fish BCG_1markexcl_noAgeClass.

# LowerBoiseBCGCalc 0.0.0.9027 (2026-07-09)

* refactor: New required fields included in FB output.

# LowerBoiseBCGCalc 0.0.0.9026 (2026-07-08)

* refactor: Added new required input fields in File Builder

# LowerBoiseBCGCalc 0.0.0.9025 (2026-07-08)

* refactor: Updated UI documentation for about, FB, and calc pages

# LowerBoiseBCGCalc 0.0.0.9024 (2026-07-08)

* docs: Removed Rproj.user folder and added to gitignore

# LowerBoiseBCGCalc 0.0.0.9023 (2026-07-08)

* docs: Removed Rproj.user folder and added to gitignore

# LowerBoiseBCGCalc 0.0.0.9022 (2026-06-03)

* docs: Update missing entries in NEWS
* docs: Update version number in DESCRIPTION
* refactor: Update version number in global
* fix: Add check for non-standard Index_Class in File Builder
    + Change right before save
* refactor: Added placeholder in File Builder for checking for duplicate user
selected column names

# LowerBoiseBCGCalc 0.0.0.9021 (2026-05-28)

* UI updates

# LowerBoiseBCGCalc 0.0.0.9020 (2026-05-28)

* Minor update that fixes output folder. Still need to deal with duplicate from calc section.

# LowerBoiseBCGCalc 0.0.0.9019 (2026-05-28)

* Removed unnecessary files from past versions

# LowerBoiseBCGCalc 0.0.0.9018 (2026-05-28)

* Updated UI

# LowerBoiseBCGCalc 0.0.0.9017 (2026-05-27)

* UI updates to About tabs and Calculate tab.

# LowerBoiseBCGCalc 0.0.0.9016 (2026-05-27)

* Additional files in www

# LowerBoiseBCGCalc 0.0.0.9015 (2026-05-27)

* Preliminary updates to About UI RMD. Added images and files so links are live.

# LowerBoiseBCGCalc 0.0.0.9014 (2026-05-27)

* fix: Update fish age class xtab to avoid crashing if don't have all classes
    + Added max possible
    + All values 0 when don't occur
        - Complete not working to get NA

# LowerBoiseBCGCalc 0.0.0.9013 (2026-05-26)

* refactor: Update to pick up changes in BCGcalc Rules.xlsx for metric sort
* refactor: Move AgeClass xtab from taxa translator to results
* refactor: Update _user_input and results_BCG output folders to include community (Bugs or Fish)
* refactor: Modify BCG_3metmemb_xtab_MetricSort.csv to include new sort values from Rules.xlsx in BCGcalc
* refactor: Update import of Rules.xlsx to avoid sort column as logical
* refactor: Add xtab Fish_AgeClass_pClasses.csv
* refactor: Update Fish_AgeClass_xtab.csv from 0 to NA when age class not possible for that taxon

# LowerBoiseBCGCalc 0.0.0.9012 (2026-05-21)

* fix: Update for revision to BioMonTools to fix metric calc
    + pi_dom01_BCG_att456t

# LowerBoiseBCGCalc 0.0.0.9011 (2026-05-21)

* docs: Add directions to README to run shiny app directly from GitHub
   
# LowerBoiseBCGCalc 0.0.0.9010 (2026-05-21)

* refactor: Update UI
   + Hide unwanted tabs

# LowerBoiseBCGCalc 0.0.0.9009 (2026-05-21)

* refactor: Modify BCG_3metmemb_xtab columns
* refactor: Modify order of columns in BCG Results file
* fix: Modify QC check for missing INDEX_NAME in File Builder

# LowerBoiseBCGCalc 0.0.0.9008 (2026-05-20)

* docs: Add shiny app URL to readme

# LowerBoiseBCGCalc 0.0.0.9007 (2026-05-20)

* refactor: Update age class xtab for RIS == TRUE
* refactor: Add membership xtab to BCG results

# LowerBoiseBCGCalc 0.0.0.9006 (2026-05-20)

* fix: Update BCGcalc package for update to Fish Main_Exckert rules

# LowerBoiseBCGCalc 0.0.0.9005 (2026-05-20)

* refactor: Add cross tab table for age class to fish output for file builder

# LowerBoiseBCGCalc 0.0.0.9004 (2026-05-20)

* docs: Add missing packages to global.R
    + kableExtra
    + rsconnect
    
# LowerBoiseBCGCalc 0.0.0.9003 (2026-05-20)

* refactor: Update version number to global
* refactor: Use revised versions of packages
    + BioMonTools
    + BCGcalc
* docs: Add "_tests" folder
* docs: Add "_tests" folder to gitignore
* refactor: Update error catching for mismatch or blank Index_Name
    + Bugs and Fish
    + FileBuilder and BCG Calculation

# LowerBoiseBCGCalc 0.0.0.9002 (2026-02-01)

-   Added File Builder function to join fish lengths to age via lookup
    
# LowerBoiseBCGCalc 0.0.0.9000 (2025-12-31)

-   Created GitHub repository
-   docs: Add base package files from GreatPlainsBCGCalc (Blocktt)
    -   DESCRIPTION
    -   NEWS
    -   README
    -   app function
